### 2024-11-17 README.Rmd
Improved the documentation and fixed an issue with the Cycle 2 (1986) episode weights, which did not correctly use the number of decimals indicated in the user's guide

The goal of ActiveCA is to ...

@@

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(ActiveCA)
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

>>>>

{ActiveCA} is an open data product in the form of an `R` data package with information about active travel in Canada. The data product is based on Public Use Microdata Files of Statistics Canada's [General Social Survey (GSS) program](https://www150.statcan.gc.ca/n1/pub/45-25-0001/index-eng.htm) with a focus on the [Time Use Survey](https://www150.statcan.gc.ca/n1/pub/45-25-0001/index-eng.htm#a7) cycles.

To reduce the barriers to the use of the Public Use Microdata Files, this data product has extracted all walking and cycling episodes and their corresponding episode weights. Origins and destinations are categorized, and it is possible to investigate active travel (number of episodes and their duration) for broad categories of purposes (e.g., travel to work or school, travel to other's home).

The data covers cycles Cycles 2 (1986), 7 (1992), 12 (1998), 19 (2005), 24 (2010), and 29 (2015), spanning a period of almost thirty years.

@@
